META II \\ \large A Syntax-Oriented Compiler Writing Language

### 2017-01-09 doc/paper.tex
fix minor typos in paper
fix Fig 6 flowing over end of page
minor typo
META II: add missing EX1 statement to self-compiler
VALGOL I grammar: fix transcription error
The `IDSEQ1` delimiter is `,`, not `.`. The difference between period
and comma in the original paper is subtle.
Fix another typo in the VALGOL I grammar transcription

\documentclass[notitlepage,twocolumn]{report}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{endnotes}

@@

EXP = EXP1 ( '.*' EXP1 .OUT('EQU') / .EMPTY) .,

@@

IDSEQ = IDSEQ1 $('.' IDSEQ1) .,

@@

\begin{figure}
\caption{Order List of the VALGOL I Machine}
\begin{center}
MACHINE CODES
\end{center}
\begin{tabular}{lllp{7cm}}
  LD & AAA & LOAD & Put the contents of the address AAA on top of the
                    stack. \\
  LDL & NUMBER & LOAD LITERAL & Put the given number on top of the
                                stack. \\
  ST & AAA & STORE & Store the number which is on top of the stack
                     into the address AAA and pop up the stack. \\
  ADD & & ADD & Replace the two numbers which are on top of the stack
                with their sum. \\
  SUB & & SUBTRACT & Subtract the number which is on top of the stack
                     from the number which is next to the top, then
                     replace them by this difference. \\
  MLT & & MULTIPLY & Replace the two numbers which are on top of the
                     stack with their product. \\
  EQU & & EQUAL & Compare the two numbers on top of the stack. Replace
                  them by the integer 1, if they are equal, or by the
                  integer 0, if they are unequal. \\
  B & AAA & BRANCH & Branch to the address AAA. \\
  BFP & AAA & BRANCH FALSE AND POP & Branch to the address AAA if the
                                     top term in the stack is the
                                     integer 0. Otherwise, continue in
                                     sequence. in either case, pop up
                                     the stack. \\
  BTP & AAA & BRANCH TRUE AND POP & Branch to the address AAA if the
                                    top term in the stack is not the
                                    integer 0. Otherwise, continue in
                                    sequence. in either case, pop up
                                    the stack. \\
  EDT & STRING & EDIT & Round the number which is on top of the stack
                        to the nearest integer n. Move the given
                        string into the print area so that its first
                        character falls on print position n. In case
                        this would cause characters to fall outside
                        the print area, no movement takes place. \\
  PNT & & PRINT & Print a line, then space and clear the print
                  area. \\
  HLT & & HALT & Halt. \\
\end{tabular}
\begin{center}
CONSTANT AND CONTROL CODES
\end{center}
\begin{tabular}{lllp{7cm}}
  SP & N & SPACE & N = 1--9. Constant code producing N blank
                   spaces. \\
  BLK & NNN & BLOCK & Produces a block of NNN eight character
                      words. \\
  END & & END & Denotes the end of the program. \\
\end{tabular}
\end{figure}

@@

@@

PROGRAM = '.SYNTAX' .ID .OUT('ADDR' *)
$ ST '.END' .OUT('END').,

@@

\begin{figure}

@@

@@

@@

\begin{center}
CONSTANT AND CONTROL CODES
\end{center}

@@

>>>>

\documentclass[notitlepage,twocolumn]{report}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{endnotes}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}

@@

EXP = EXP1 ( '.=' EXP1 .OUT('EQU') / .EMPTY) .,

@@

IDSEQ = IDSEQ1 $(',' IDSEQ1) .,

@@

\begin{figure}
\caption{Order List of the VALGOL I Machine}
\begin{center}
MACHINE CODES
\end{center}
\begin{tabular}{lllp{7cm}}
  LD & AAA & LOAD & Put the contents of the address AAA on top of the
                    stack. \\
  LDL & NUMBER & LOAD LITERAL & Put the given number on top of the
                                stack. \\
  ST & AAA & STORE & Store the number which is on top of the stack
                     into the address AAA and pop up the stack. \\
  ADD & & ADD & Replace the two numbers which are on top of the stack
                with their sum. \\
  SUB & & SUBTRACT & Subtract the number which is on top of the stack
                     from the number which is next to the top, then
                     replace them by this difference. \\
  MLT & & MULTIPLY & Replace the two numbers which are on top of the
                     stack with their product. \\
  EQU & & EQUAL & Compare the two numbers on top of the stack. Replace
                  them by the integer 1, if they are equal, or by the
                  integer 0, if they are unequal. \\
  B & AAA & BRANCH & Branch to the address AAA. \\
  BFP & AAA & BRANCH FALSE AND POP & Branch to the address AAA if the
                                     top term in the stack is the
                                     integer 0. Otherwise, continue in
                                     sequence. In either case, pop up
                                     the stack. \\
  BTP & AAA & BRANCH TRUE AND POP & Branch to the address AAA if the
                                    top term in the stack is not the
                                    integer 0. Otherwise, continue in
                                    sequence. In either case, pop up
                                    the stack. \\
  EDT & STRING & EDIT & Round the number which is on top of the stack
                        to the nearest integer n. Move the given
                        string into the print area so that its first
                        character falls on print position n. In case
                        this would cause characters to fall outside
                        the print area, no movement takes place. \\
  PNT & & PRINT & Print a line, then space and clear the print
                  area. \\
  HLT & & HALT & Halt. \\
\end{tabular}
\begin{center}
CONSTANT AND CONTROL CODES
\end{center}
\begin{tabular}{lllp{7cm}}
  SP & N & SPACE & N = 1--9. Constant code producing N blank
                   spaces. \\
  BLK & NNN & BLOCK & Produces a block of NNN eight character
                      words. \\
  END & & END & Denotes the end of the program. \\
\end{tabular}
\end{figure}

@@

EX1 = EX2 $('/' .OUT('BT ' *1) EX2 )
.LABEL *1 .,

@@

PROGRAM = '.SYNTAX' .ID .OUT('ADR' *)
$ ST '.END' .OUT('END').,

@@

\begin{figure}[htb]

@@

  \begin{subfigure}[b]{\textwidth}
    \subcaption{MACHINE CODES}

@@

  \end{subfigure}
\begin{figure}[htb]\ContinuedFloat
  \begin{subfigure}[b]{\textwidth}

@@

  \end{subfigure}
  \begin{subfigure}[b]{\textwidth}
    \subcaption{CONSTANT AND CONTROL CODES}

@@

  \end{subfigure}
